Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-13 cvpr2018.tex
replae bird with flower

\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images (up to $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial training strategy at multiple nested side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics. 
\end{abstract}

@@

\begin{figure}[t]
%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
	\end{subfigure} \\
\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
	\end{subfigure}
	\vspace{-.6cm}
	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained generated results. \label{fig:intro}} 	
	\vspace{-.8cm}
	%\end{center}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful two-state training approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in a fully end-to-end manner is still an open and attractive question.

%We outline several empirical reasons for the challenges of 
Text-to-image synthesis using GANs has two main difficulties. The first is the fundamental problem of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
To guarantee the image diversity and semantic consistency,
\textcolor{red}{we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.}
This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics. All source code will be released.

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution extensions. Wide methods have been proposed to address the training instability, through various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not use any extra information apart from training paired text and images.} Additionally, it is easy to see the training difficulty increases significantly as targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from the last pyramid level, and thereby push up the output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these families of CNNs with deep supervision. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z)
\end{split}
\end{equation}
\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The value function $\mathcal{V}$ aims to minimize the Jensen-Shannon divergence between the data and the model distribution. $G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. }

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
To satisfy this goal, we present the following adversarial loss to support more effective multi-purpose discriminators. Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN (see experiments). }

@@

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.5cm}
	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to classify real or fake patches). The focal range increases as image resize grows. Lower range results in finer results. }  \vspace{-.3cm}
	\label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following loss\footnote{The objective of the generator is omitted as it can be easily inferred.}:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big)
\end{split}
\end{equation}
where $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =x^2$. For local image loss with varying focal ranges, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}). $R=1$ refers to the (largest local) global range. For the matching-aware pair loss, 
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

@@

\subsection{Training Details}
%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
The Adam optimizer is used for all experiments.  The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO). The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
For the local image loss, we set $R=1$ and for $64^2$ and $128^2$ side outputs and $R=5$ for $256^2$ and $512^2$ outputs.
We use 1-repeat residual block for the generator till $256^2$ resolution.
\textcolor{red}{To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory. We use $3$-repeat res-block followed by the stretching and linear compression layer. 
Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we use a l1 reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
%for the consideration of memory saving and faster convergence.

@@

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and Oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model pre-trained on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance. 3) Visual-semantic similarity.

@@

\begin{figure*}[t]
	%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.69\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/multisample_cub.pdf}
	\end{subfigure} 
	\begin{subfigure}[t]{0.3\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/cub_multires.pdf}
	\end{subfigure}
	\vspace{-.2cm}
	\caption{Left: Diversity test given a single input text. The proposed HDGAN (top) show obviously more details and higher diversity. Right: Side outputs of HDGAN with increasing resolutions. Different resolutions are semantically consistent and semantic details emerges as resolution increases.  \label{fig:multiple-test}} 	\vspace{-.3cm}
	%\end{center}
\end{figure*}

>>>>

\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images (up to $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics. 
\end{abstract}

@@

\begin{figure}[t]
%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth]{figure/intro.pdf}
	\end{subfigure} \\
\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
	\end{subfigure}
	\vspace{-.6cm}
	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained sample results. \label{fig:intro}} 	\vspace{-.3cm}
	%\end{center}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an fully end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
To guarantee the image diversity and semantic consistency,
\textcolor{red}{we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.}
This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of the image diversity evaluation metric (inception score \cite{improvedGAN}), we introduce a new visual-semantic similarity measurement to evaluate th alignment between generated images and corresponded text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics. All source code will be released.

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from low-dimensional embeddings to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many  unsolved difficulties, e.g. training instability and high-resolution extensions. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}. \textit{While our method does not use any extra information apart from training paired text and images.} Moreover, it is easy to see the training difficulty increases significantly as targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from the last pyramid level, and thereby push up the output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these kinds of CNNs with deep supervision. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
\end{split}
\end{equation}
\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions. }

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN. More results can be founded in experiments. 
According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}

@@

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and is trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.2cm}
	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches). The focal range increases as image resize grows. Lower range results in finer results. }  \vspace{-.3cm}
	\label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our hierarchically-nested discriminators $\{D_i\}$ minimize the following objective\footnote{The objective of the generator is omitted as it can be easily inferred.}:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{L}(& \mathcal{G}, \mathcal{D})  = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big)
\end{split}
\end{equation}
where ${X}_i = \mathcal{G}(\bm{t}_{X}, \bm z)$. $L_2(x) = (x - \mathbb{I})^2$ is the mean-square loss (we do not use the original cross-entropy loss) and $\overline{L_2}(x) =(x)^2$. For adaptive local image loss with varying focal range, the shape of $x, \mathbb{I} \in \mathbb{R}^{R{\times}R}$ varies accordingly (see Figure \ref{fig:loss}) for the local image loss. $R=1$ refers to the (largest local) global range, e.g., $R\equiv1$ for the matching aware pair loss. For the matching-aware pair loss, 
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

@@

\subsection{Training Details}
%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
The Adam optimizer is used for all experiments.  The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO). The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO).
For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
We use 1-repeat residual block for the generator till $256^2$ resolution.
\textcolor{red}{To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory. We use $3$-repeat res-block followed by the stretching and linear compression layer. maybe delete the l1 loss description.
Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.}
%for the consideration of memory saving and faster convergence.

@@

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model pre-trained on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance. 3) Visual-semantic similarity.

@@

\begin{figure*}[t]
	%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.69\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/multisample_cub.pdf}
	\end{subfigure} 
	\begin{subfigure}[t]{0.3\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/cub_multires.pdf}
	\end{subfigure}
	\vspace{-.2cm}
	\caption{Left: Diversity test given a single input text. HDGAN (top) show obviously more details and higher diversity. Right: Side outputs of HDGAN with increasing resolutions. Different resolutions are semantically consistent and semantic details emerges as resolution increases.  \label{fig:multiple-test}} 	\vspace{-.3cm}
	%\end{center}
\end{figure*}
